Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach

### 2024-11-04 paper/paper.qmd
Updated title and caption

---
title: "Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach"
subtitle: "Kamala Harris Poised for Victory"
author: 
  - Xinxiang Gao
  - Ariel Xing
  - John Zhang^[The authors are listed in alphabetical order by last name.]
thanks: "Code and data are available at: [https://github.com/xgao28/election_forecast](https://github.com/xgao28/election_forecast)."
date: today
date-format: long
abstract: "The upcoming U.S. Presidential Election on November 5th features a closely contested race between Vice President Kamala Harris and former President Donald Trump. This paper uses a poll-of-polls approach, combined with a dynamic linear regression model that updates daily with the latest data, to forecast the popular vote and outcomes in seven battleground states: Arizona, Georgia, Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania. Our analysis currently projects that Vice President Harris will win the popular vote, 48.19% to 46.01%, and secure the electoral college with 292 votes to Trump’s 246, by winning five of these seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania. By aggregating multiple polls rather than relying on a single poll, our model provides a more robust prediction, supporting the likelihood of a Harris victory."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

![Result](../other/photos/Predicted_Result.png){#fig-result}

@@

![YouGov Welcome Page](../other/photos/YouGov_Welcome_Page.png){#fig-YouGovWelcomePage width=60%}

@@

![YouGov Survey](../other/photos/YouGov_Survey.png){#fig-YouGovSurvey width=60%}

@@

![YouGov Email Verification](../other/photos/YouGov_Email_Verification.png){#fig-YouGovEmailVerification width=60%}

@@

![YouGov Data Privacy](../other/photos/YouGov_Data_Privacy.png){#fig-YouGovDataPrivacy width=60%}

@@

![YouGov Interface](../other/photos/YouGov_Interface.png){#fig-YouGovInterface width=60%}

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach"
subtitle: "Kamala Harris Projected to Win the Electoral College with 292 Votes to Donald Trump’s 246"
author: 
  - Xinxiang Gao
  - Ariel Xing
  - John Zhang^[The authors are listed in alphabetical order by last name.]
thanks: "Code and data are available at: [https://github.com/xgao28/election_forecast](https://github.com/xgao28/election_forecast)."
date: today
date-format: long
abstract: "The upcoming U.S. Presidential Election on November 5th features a closely contested race between Vice President Kamala Harris and former President Donald Trump. This paper uses a poll-of-polls approach, combined with a dynamic linear regression model that updates daily with the latest data, to forecast the popular vote and outcomes in seven battleground states: Arizona, Georgia, Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania. Our analysis currently projects that Vice President Harris will win the popular vote, 48.19% to 46.01%, and secure the electoral college with 292 votes to Trump’s 246, by winning five of these seven swing states: Nevada, North Carolina, Michigan, Wisconsin, and Pennsylvania. By aggregating multiple polls rather than relying on a single poll, our model provides a more robust prediction, supporting the likelihood of a Harris victory."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

![Projected Electoral College Results for the 2024 U.S. Presidential Election, with Kamala Harris Expected to Secure 292 Electoral Votes Against Donald Trump’s 246](../other/photos/Predicted_Result.png){#fig-result}

@@

![Initial welcome screen during YouGov onboarding, confirming country of residence and introducing users to the platform's privacy policies and terms](../other/photos/YouGov_Welcome_Page.png){#fig-YouGovWelcomePage width=60%}

@@

![Example of a YouGov survey question, designed to gather demographic information and establish privacy preferences, fostering user engagement through a clear and straightforward layout](../other/photos/YouGov_Survey.png){#fig-YouGovSurvey width=60%}

@@

![Email verification screen to confirm user identity, enhancing data integrity by preventing duplicate or fraudulent accounts](../other/photos/YouGov_Email_Verification.png){#fig-YouGovEmailVerification width=60%}

@@

![Data privacy options allowing users to control the sharing of their information with third parties, reflecting YouGov’s commitment to transparency and user autonomy](../other/photos/YouGov_Data_Privacy.png){#fig-YouGovDataPrivacy width=60%}

@@

![Overview of YouGov’s gamified rewards system, where participants accumulate points redeemable for gift cards, potentially motivating user engagement with surveys](../other/photos/YouGov_Interface.png){#fig-YouGovInterface width=60%}
